A note on multi agent learning

### 2016-06-28 multiAgentLearning/paper/article.tex
added a intermezzo

\section{Satisficing play in action}
\todo{make an intermezzo of this?}
\drafting
To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoner's dilemma. Consider
the following normal form game:

\todo{add table caption}
\begin{tabular}{lll}
            & Cooperate   & Defect \\
  Cooperate & $(2,2)$     & $(0,3)$  \\
  Defect    & $(3,0)$     & $(1,1)$  \\
\end{tabular}

\drafting The Nash equilibrium of this game lies on Defect,Defect. However, all but
that action are pareto optimal actions. So the Nash equilibrium would be the
``right'' strategy to play if the game is only played once, but if you repeat
the game against the same opponent, interestingly enough you can ``solve''
the prisoner's dilemma by ``teaching'' the opponent to cooperate.
\todo{can one really solve? Is it really teaching? should either add references
or change wording}

\drafting However strategies such as tit for tat or win stay lose shift already know
which actions are winning and which are punishing to try and solve it.
Satisficing play learns this however by updating the aspiration it got from
playing a move. If we consider a game versus always cooperate for example:

>>>>

\section{Satisficing play in action}
\todo{make an intermezzo of this?}
\drafting
To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoner's dilemma.
\fbox{
  \begin{minipage}{2.5in}
    \subsection{A prisoner's dillema introduction}
    The prisoner's dillema is one of the classical game thoery examples.
    Consider the following normal form game which is a prisoner's dillema:
    \begin{tabular}{lll}
                & Cooperate   & Defect \\
      Cooperate & $(2,2)$     & $(0,3)$  \\
      Defect    & $(3,0)$     & $(1,1)$  \\
    \end{tabular}
    The Nash equilibrium of this game lies on (Defect,Defect). However, all but
    that action are pareto optimal actions. So the Nash equilibrium would be the
    ``right'' strategy to play if the game is only played once, but if you repeat
    the game against the same opponent, interestingly enough you can ``solve''
    the prisoner's dilemma by ``teaching'' the opponent to cooperate.
    \todo{can one really solve? Is it really teaching? should either add references
    or change wording}
	\end{minipage}
	}
\drafting However strategies such as tit for tat or win stay lose shift already know
which actions are winning and which are punishing to try and solve it.
Satisficing play learns this however by updating the aspiration it got from
playing a move. If we consider a game versus always cooperate for example:
